The Driving Forces of API Evolution

### 2015-05-21 thesis/paper.tex
Updated abstract

% \textbf{Background  } %Give a feeling of the need of this study, answer why the case company needs what is in the Objective (+Context)
% The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored. Previous studies have not considered APIs from the perspective of well-established software evolution theories.

% \smallskip \noindent
% \textbf{Objective  } %Done
% In this study, we explore how companies actively evolve their APIs and 'how APIs evolve from a passive point of view'. We also aim to evaluate to what extent we are able to reverse engineer these evolutionary change decisions. The goal is to study these factors by evaluating them against existing software evolution theories.

% \smallskip \noindent
% \textbf{Method  } %Done
% This case study was conducted by analysing the changes between two versions of a platform API and its documentation. The results were analysed from a qualitative and investigative perspective, and were then reviewed and validated with the architects of the API.

% \smallskip \noindent
% \textbf{Results  } %Done
% We identified thirteen major changes which were introduced in the new version of the API. We concluded that the dominant driving force of the API evolution is demand for new functionality and that change decisions, to a large extent, are reverse engineerable. We also found that long-established software evolution laws were largely applicable to APIs.

% \smallskip \noindent
% \textbf{Conclusion  }
% This study has provided valuable insight into the evolution of platform APIs. The qualitative analysis can help other companies to improve their API maintenance process. The successful attempt to reverse engineer the change decisions should encourage similar studies to be conducted. The investigation of Lehman's laws show that APIs cannot be generalised and be compared to any type of system.

%Background and need for study, make it interesting

%Other studies
Other studies have investigated why changes occur to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of the API according to software evolution theories. Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.
% How do we do it?
Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
% Our results and future suggestions
The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality. It highlighted the fact that not all software evolution theories are applicable to APIs. We found that changes happen sporadically rather than slowly over time and the contradiction of a software evolution law that states the opposite is true. The research further supported the importance of a feedback loop of a software system, which is something that company A also wants. The study concludes by proposing suggestions for future studies based on our findings.

>>>>

%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
% %Background and need for study, make it interesting
% Evolving a software system is a precipitous activity. Many software evolution theories have been created to assist changing systems. However, as modern systems are making greater use of APIs, do these software evolution theories apply to them?
% %Other studies
% Other studies have investigated why changes are made to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of an API according to software evolution theories. Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.
% % How do we do it?
% Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
% % Our results and future suggestions
% The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality. It highlighted the fact that not all software evolution theories are applicable to APIs. We found that changes happen sporadically rather than slowly over time and the contradiction of a software evolution law that states the opposite is true. The research further supported the importance of a feedback loop of a software system, which is something that company A also wants. The study concludes by proposing suggestions for future studies based on our findings.
%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

%What I did: 
       %Tried to make the motivation/purpose more clear/'''''''crisp''''''''''
       %Removed the background/other studies stuff. Don't think that's needed in abstract.
       %Made it a bit more bold/selling
       %Re-worded the results a bit
       %Removed the last sentence, don't think we have to mention that we propose future work (since everyone does)

%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
%Motivation/Purpose
       %Why did you decide to do this study?
       %Why is this research important?
       %Why should someone read your entire study?
Evolving an API is a precipitous activity, mainly because of the great implications modifications to it can have on the users of it. As modern systems are making greater use of APIs, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs. 
%Problem Statement
       %What is your research trying to better understand or solve?
       %What is the scope of your study - a general problem, or something specific?
       %What is your main claim or argument?
If no attempt at analysing or quantifying the evolution of an API is undertaken, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify. We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs. 
%We believe, that by analysing APIs using existing software evolution theories, one can solve this problem. 
%Method
In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code. The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the designer of the API. 
%Results
The results of this analysis show that the largest driving force of API evolution is the desire for new functionality. Our findings which show that changes happen sporadically, rather than continuously,invalidate a law of software evolution, in the context of APIs. We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement. 
%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

%Stuff that should be improved:
       %double 'it' in first sentence
       %Greater use = more ppl use?
       %does undertaken fit with attempt
       %It's 239 words now... should try to cut it to 200. (maybe 2nd sentence of method can be removed) (maybe results can be shortened a bit)
